\section*{Acknowledgements}
\label{acknowledge}

        Many people collaborated on the research described  in this thesis.
In particular I would like  to thank Jagadeesh Moodera, Eric  Tkaczyk, Paul
Tedrow, and Mike Blaho of the Francis Bitter National Magnet Laboratory for
many hours of  assistance  with the   low-temperature experiments.  Special
thanks     go to Mike   Blaho for    straightening  the  (ahem) bent $^3$He
refrigerator.   The high-field experiments could   not have been  performed
without the assistance of  Nai-chang Yeh and Bruce Brandt.

        The neutron diffraction experiments were  performed at the National
Bureau of  Standards  reactor  in   collaboration with  Dan  Neumann,  Bill
Kamitakahara, and Ann Bouchard.   The advice of  Dan and Bill regarding the
data analysis   was invaluable.   Nagel Stone  machined  the neutron sample
cells, and also provided a lot of useful advice over the years.

        Gerhard  Roth   and   Mar\'{\i}a    Kudisch assisted  with   sample
preparation  and x-ray characterization  in the early  part of the  KHg-GIC
study.    Dr.   Toshiaki Enoki   of the    Tokyo  Institute of   Technology
participated  in the  early hydrogenation experiments.   Many  of the ideas
concerning the hydrogenation experiments come either from his advice or his
publications.

      Of the students in the MGM research group, I would especially like to
thank  Jim Speck for   answering  so   many  elementary  materials  science
questions  about  metallurgy and  structural analysis.   Thanks  also go to
James Nicholls  for assistance in performing  resistivity measurements, and
Gary Doll and Yachin Liu for taking the Raman  data.  Gary greatly improved
our methods  of GIC  synthesis when  he  arrived, so all  the  work on  the
KHg-GIC's has  benefitted from  his expertise.  He  also built the hydrogen
train which was used in the later stages  of the hydrogenation experiments.
Special thanks go to James, Gary, and Jim  for  timely loans  of equipment,
some of which was even borrowed with their consent.

        This thesis could  not have been written without  Gene Dresselhaus,
Lt. John Steinbeck, Eliot Dresselhaus, and  Paul Dresselhaus, who  kept the
VAX running  most  of the  time.   Eliot supplied  the text processing  and
graphics software with which this document and its figures were produced.

        Most of all I would like to  thank Wolfgang  Rupprecht,  partly for
tangible   favors   like  explaining electronics,   debugging  my  computer
programs,  and making lots  of  tea.  I would  especially   like  to  thank
Wolfgang for encouragement when I most needed it.

        Finally, I would like to express my  gratitude to  the teachers who
made my experience in graduate school  worthwhile.  Frank  Payne has always
been very generous  with his time, and  he  puts  a lot   more  effort than
necessary into teaching  students about  machining.  Terry Orlando and Paul
Tedrow  provided  a great  deal   of expert  advice   about  the  theory of
superconductivity and data  analysis.    Professors  Joannopolous,   Jaffe,
Tinkham and  Jackiw taught  courses    which were not  only  valuable   but
inspirational.  I also learned a great deal from the many courses taught by
my thesis  supervisor, Mildred  Dresselhaus.   I would  like  to express my
gratitude to Millie and to Gene Dresselhaus  for their knowledge, expertise
and guidance.
